### 2021-04-07 Chapter-2/Chapter-2.tex
Updates from Overleaf

Model counting refers to the problem of computing the number of satisfying
solutions for a propositional formula (\#SAT). There are two approaches to
solving the problem, exact model counting and approximate model
counting. Exact model counting for propositional formulas (\#SAT) should determine
the number of solutions. Intuitively, such model counter should traverse the whole
search space to find all the satisfying solutions. Consequently, exact model counter is 
 very slow. Those model counters have difficulty scaling up to real-world programs.
We focus on approximate model counting since it is our approach. Wei and Selman~\cite{wei2005new} introduce
ApproxCount, a local search based method using Markov Chain Monte
Carlo (MCMC). ApproxCount has the better scalability than
exact model counters. Other approximate model counter includes
SampleCount~\cite{gomes2007sampling},
Mbound~\cite{gomes2006model}, and MiniCount~\cite{kroc2008leveraging}.
Unlike ApproxCount, these model counters can give lower or upper bounds with guarantees.
Despite the rapid development of model counters for SAT and some
research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT), existing tools cannot be directly applied to side channel leakage quantification.
ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.

>>>>

Model counting refers to the problem of computing the number of satisfying
solutions for a propositional formula (\#SAT). There are two approaches to
solving the problem, exact model counting and approximate model
counting. Exact model counting for propositional formulas (\#SAT) should determine
the number of solutions. Intuitively, such model counter should traverse the whole
search space to find all the satisfying solutions. Consequently, exact model counter is 
very slow. Those model counters have difficulty scaling up to real-world programs.
On the other hand, approximate model counter is much faster compared with the exact 
model counter. The related work focus on approximate model counting since it is close to our approach. Wei and Selman~\cite{wei2005new} introduce
ApproxCount, a local search based method using Markov Chain Monte
Carlo (MCMC). ApproxCount has the better scalability than
exact model counters. Other approximate model counter includes
SampleCount~\cite{gomes2007sampling},
Mbound~\cite{gomes2006model}, and MiniCount~\cite{kroc2008leveraging}.
Unlike ApproxCount, these model counters can give lower or upper bounds with guarantees.
Despite the rapid development of model counters for SAT and some
research~\cite{chistikov2017approximate,phan2015model}, existing tools cannot be directly applied to side channel leakage quantification for the following two reasons.
ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.
